A weighted data representation based approach for manifold learning

### 2018-11-06 DimReduction/Lle/Documentation/Article_lle.tex
Adding conclusion section to Lle documentation

In this work

>>>>

In this work a theorical and practical develop of the local linear embeding
algorithm was described. During the process it was found that althought the
problems started with a quite complicated setup, the development of the problem
allowed to generate great simplifications that reduced the original problem to
just solve a linear system of equations and an eigenvector problem. These
simplifications made possible the creation of a relatively simple algorithm that
can detect low dimensional manifolds in multidimensional spaces. This statement
is supported in the results section where 3 dimensional manifolds were
simplified to dimension 2 but preserving the intrinsic structure of the original
dataset.
